Tidal Locking in Low-Mass Stellar Binary Stars

### 2018-11-09 Paper/sync.tex

@@

Rotation period distributions measured in clusters and field stars are likely contaminated by unresolved binaries, given that roughly half of Sun-like stars are in stellar binaries \citep{Raghavan2010,Duchene2013}, and that binaries are difficult to resolve in photometric surveys due to low transit probabilities. In the \kepler field, for example, \citet{Simonian2018} recently found that most rapid rotators (P$_{rot} \lsim 7.5$ d) are likely non-eclipsing, tidally-synchronized short-period photometric binaries, indicating that tidal torques in binaries can significantly impact observed P${rot}$ distributions.  Even if stellar binaries have not yet tidally-locked, tidal torques modify stellar rotation periods away from the long-term spin-down due to magnetic braking predicted for single stars \citep{Dunn1961,Skumanich1972,Barnes2003}. Ages inferred from rotation periods of stars in unresolved binaries using gyrochronology, a method that link the long-term spin-down of low-mass stars to their ages, \citep{Skumanich1972,Barnes2003,Barnes2007,Mamajek2008,Barnes2010}, will likely be incorrect, however no previous study has quantified this effect.  Moreover, no previous study has quantified how tidal-locking proceeds in low-mass stellar binaries using a realistic treatment of stellar evolution and magnetic braking.

XXX mention main sequence lifetimes

@@

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/example.pdf}
   \caption{Caption}%
    \label{fig:lockingCPL}%
\end{figure}

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/example.pdf}
   \caption{Caption}%
    \label{fig:lockingCTL}%
\end{figure}

>>>>

- Consult Lurie's paper for CPL vs CTL (e.g. why not 3:2 population-> use CTL!) and for discussing sunsync population

@@

Rotation period distributions measured in clusters and field stars are likely contaminated by unresolved binaries, given that roughly half of Sun-like stars are in stellar binaries \citep{Raghavan2010,Duchene2013}, and that binaries are difficult to resolve in photometric surveys due to low transit probabilities. In the \kepler field, for example, \citet{Simonian2018} recently found that most rapid rotators (P$_{rot} \lsim 7.5$ d) are likely non-eclipsing, tidally-synchronized short-period photometric binaries, indicating that tidal torques in binaries can significantly impact observed P${rot}$ distributions.  Even if stellar binaries have not yet tidally-locked, tidal torques modify stellar rotation periods away from the long-term spin-down due to magnetic braking predicted for single stars \citep{Dunn1961,Skumanich1972,Barnes2003}. Ages inferred from rotation periods of stars in unresolved binaries using gyrochronology, a method that link the long-term spin-down of low-mass stars to their ages, \citep{Skumanich1972,Barnes2003,Barnes2007,Mamajek2008,Barnes2010}, will likely be incorrect, however no previous study has quantified this effect.  Moreover, no previous study has quantified how tidal-locking proceeds in stellar binaries using a realistic treatment of stellar evolution and magnetic braking over the full main sequence lifetimes of low-mass stars.

@@

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/lockedCPL.pdf}
   \caption{Caption}%
    \label{fig:lockingCPL}%
\end{figure}

\begin{figure}[h]
	\includegraphics[width=0.45\textwidth]{../Plots/lockedCTL.pdf}
   \caption{Caption}%
    \label{fig:lockingCTL}%
\end{figure}
